### 2023-02-09 paper-thesis/chapters/02-background-spoofax.tex
Minor fixes

\section{Statix}
Now that the syntax has been determined, we move on to the static semantics. Statix is a declarative language for describing the static semantics of a language~\cite{scopes_as_types}. Using these rules, Statix automatically derives a type checker. The rules are based on \emph{equality constraints}. The basic constraints
are equality constraints \verb|t1 == t2| and inequality constraints \verb|t1 != t2| on terms. An equality constraint is states that two terms are equal or can be unified. An inequality constraint states that two terms are not equal.

The constraints are generated by predicates. A predicate defines a relation on terms and scopes, it is of the form $\mathtt{p(t_1, ..., t_n) :- c_1, ..., c_n}$. Each constraint $c_1...c_n$ is another predicate or an equality constraint. Below is an example that uses these mechanics to check that an expression does not contain any \verb|Muls|. Note that \verb|noMuls| is not defined for the \verb|Mul| constructor, so it will fail if it encounters one.
\begin{lstlisting}
noMuls(Add(e1, e2)) :- noMuls(e1), noMuls(e2).
noMuls(X()).
\end{lstlisting}

>>>>

\section{Statix}
Now that the syntax has been determined, we move on to the static semantics. Statix is a declarative language for describing the static semantics of a language~\cite{scopes_as_types}. Using these rules, Statix automatically derives a type checker.  The two basic constraints that can be used in the rules are equality constraints \verb|t1 == t2| and inequality constraints \verb|t1 != t2|. An equality constraint is states that two terms are equal or can be unified. An inequality constraint states that two terms are not equal.

The constraints are generated by predicates. A predicate defines a relation on terms and scopes, it is of the form $\mathtt{p(t_1, ..., t_n) :-\,\,c_1, ..., c_n}$. Each constraint $c_1...c_n$ is another predicate or an equality constraint. Below is an example that uses these mechanics to check that an expression does not contain any \verb|Muls|. Note that \verb|noMuls| is not defined for the \verb|Mul| constructor, so it will fail if it encounters one.
\begin{lstlisting}
noMuls(Add(e1, e2)) :- noMuls(e1), noMuls(e2).
noMuls(X()).
\end{lstlisting}
